### 2020-06-19 magic_paper.tex

An example of comparison between different Lorenz curves is illustrated in~\cref{fig:lctoy}. \nick{expand}
\begin{figure}
    \centering
    \includegraphics[height=5cm]{figs/lctoy.pdf}
    \caption{Example of different Lorenz curves for quasi-probability vectors under $\bmd$-majorization.
    Vectors $\bmy$ and $\bmd$ are simply probability distributions.
    The curve corresponding to vector $\bmd$ is always the line segment connecting $(0,0)$ and $(1,1)$, so that any other Lorenz curve lies above it, for example $\bmx \prec_{\bmd} \bmd$.
    Curves $L_k(\bmx|\bmd)$ and $L_k(\bmy|\bmd)$ intersect, so $\bmx \nprec_{\bmd} \bmy$ as well as $\bmy \nprec_{\bmd} \bmx$.
    \nick{Recast in terms of magic}
    }
    \label{fig:lctoy}
\end{figure}

@@

>>>>

\subsection{Lorenz curves for magic states in a $\sigma$--fragment}
With this it is straightforward to construct Lorenz curves for Wigner distributions in any $\sigma$--fragment. For any $\sigma$ being a full rank free state we have that $W_\sigma(\bmx) $ is a strictly positive full-rank probability distribution, and so one can define a corresponding notion of $d$--majorization on \emph{quasi}--distributions.We write $L_{\rho|\sigma}(x)$ for the Lorenz curve of $W_\rho(\bmx)$ with respect to $W_\sigma(\bmx)$.

We now see that $0\le L_{\rho |\sigma}(x) \le 1$ for all $x$ if and only if $\rho$ is a positive Wigner state. Moreover, the area of the function $L_{\rho|\sigma}$ above the line $y=1$ is a resource monotone in this fragment. \ddd{[expand on this -- relate to mana?]}

An example of comparison between different Lorenz curves is illustrated in~\cref{fig:lctoy}.

\begin{figure}
    \centering
    \includegraphics[height=5cm]{figs/lctoy.pdf}
    \caption{Example of different Lorenz curves for quasi-probability vectors under $\bmd$-majorization.
    Vectors $\bmy$ and $\bmd$ are simply probability distributions.
    The curve corresponding to vector $\bmd$ is always the line segment connecting $(0,0)$ and $(1,1)$, so that any other Lorenz curve lies above it, for example $\bmx \prec_{\bmd} \bmd$.
    Curves $L_k(\bmx|\bmd)$ and $L_k(\bmy|\bmd)$ intersect, so $\bmx \nprec_{\bmd} \bmy$ as well as $\bmy \nprec_{\bmd} \bmx$.
    \nick{Recast in terms of magic}
    }
    \label{fig:lctoy}
\end{figure}

@@

\subsection{Magic, Mana and Majorization}
We now discuss majorization features common to all fragments, before specialising to particular $\sigma$--fragments and how analysis in them preceeds. Mana is the basic resource monotone for magic. Here we show that its basic properties are actually special cases of more general majorization features. More precisely its properties can be viewed as majorization-based, and independent of the particular $\sigma$--fragment one works in.
